---
title: "Q2_ZHANG, XIAO_17204147"
author: "ZHANG, XIAO (17204147)"
date: "2020/6/9"
output:
  word_document: default
  html_document: default
---
```{r}
library(ggplot2)
```
##Load packages
```{r}
data <- read.csv("data.csv")
```

## Input the dataset from the local disk. The dataset contains the number of the recovered and death cases in Malaysia from 01/22/2020~06/07/2020. 


```{r}
head(data)
```

## It shows the first 6 rows in the dataset. We can see that the first column implies the date when data collected, second is the Recovered cases and third is Deaths.

```{r}
tail(data)
```

## This are the last 6 rows.

```{r}
dim(data)
```

## Now we know the dataset totally has 420 rows and 4 columns.

```{r}
input <- data[,c('Recovered', 'Deaths')]
ggplot(input, aes(x=Recovered, y=Deaths, col="#C80815" ))+geom_point()
```

## Plot a scatter plot shows the relationship between total number of the recovered and death cases.From the plot we can know that there is a strong linear relationship between those two variables.

```{r}
hist(data$Recovered,col="steelblue",xlab="Recovered Cases", main='Histogram plot for Recovered Cases ')
```

## Plot the histogram for "Recovered Cases" 

```{r}
hist(data$Deaths,col="steelblue", xlab="Deaths", main='Histogram plot for Dead Cases')
```

## Plot the histogram for "Death Cases"

```{r}
df <- data[which(rowSums(data==0)==0),]
```

## Clean the zero numbers, since too many empty values may distruct the plot.

```{r}
boxplot(Recovered~Deaths, data=df, xlab='Deaths', ylab = 'Recovered Cases', main='Boxplot for Recovered~Dead Cases', col="red")
```

## Plot a boxplot to show the realationship between Recovered and Death numbers. It indicates that those two variables has a correlated upheaval relationship. The force to rise up and get down between those two are Complementary.