---
title: "Lab7"
author: "ZHANG, XIAO (17204147)"
date: "2020/6/7"
output: html_document
---
#load library data.table
```{r}
library(data.table)
DT<-fread("./household_power_consumption.txt", na.strings="?")
```
#set date as d:m:y
```{r}
DT$strDate <- as.Date(DT$Date,"%d/%m/%Y")
```

#select data 
```{r}
DT.filter<-DT[DT$strDate=="2007-02-01" | DT$strDate=="2007-02-02",]
DT.filter$Global_active_power<-as.numeric(DT.filter$Global_active_power)
rm(DT)

```
#output histogram to PNG

```{r}
png(filename="plot1.png", width=480, height=480)
hist(DT.filter$Global_active_power, 
     col="red", 
     xlab="Global Active Power (kilowatts)", 
     main="Global Active Power")
dev.off()
```
### Plot2.R
```{r}
DT<-fread("./household_power_consumption.txt", na.strings="?")
DT$Date <- as.Date(DT$Date, format="%d/%m/%Y")
```
### Subsetting the data
```{r}
DT.filter <- subset(DT, subset=(Date >= "2007-02-01" & Date <= "2007-02-02"))
rm(DT)
```
# Converting dates
```{r}
datetime <- paste(as.Date(DT.filter$Date), DT.filter$Time)
DT.filter$Datetime <- as.POSIXct(datetime)
```
#output histogram to PNG
```{r}
plot(DT.filter$Global_active_power~DT.filter$Datetime, type="l",
     ylab="Global Active Power (kilowatts)", xlab="")
dev.copy(png, file="plot2.png", height=480, width=480)

dev.off()
```
#Plot3.R
```{r}
## Getting full dataset
DT<-fread("./household_power_consumption.txt", na.strings="?")
```

```{r}
DT$Date <- as.Date(DT$Date, format="%d/%m/%Y")
```

## Subsetting the data
```{r}
DT.filter <- subset(DT, subset=(Date >= "2007-02-01" & Date <= "2007-02-02"))
rm(DT)
```

## Converting dates
```{r}
datetime <- paste(as.Date(DT.filter$Date), DT.filter$Time)
DT.filter$Datetime <- as.POSIXct(datetime)
```

#plot the graph with legends
```{r}
with(DT.filter, {
  plot(Sub_metering_1~Datetime, type="l",
       ylab="Energy sub metering", xlab="")
  lines(Sub_metering_2~Datetime,col='Red')
  lines(Sub_metering_3~Datetime,col='Blue')
})
legend("topright", col=c("black", "red", "blue"), lty=1, lwd=2,
       legend=c("Sub_metering_1", "Sub_metering_2", "Sub_metering_3"), cex = 0.75)
```
## output histogram to PNG
```{r}
dev.copy(png, file="plot3.png", height=480, width=480)
dev.off()
```
## Plot4.R
## Getting full dataset
```{r}
DT<-fread("./household_power_consumption.txt", na.strings="?")
```

```{r}
DT$Date <- as.Date(DT$Date, format="%d/%m/%Y")
```
## Subsetting the data
```{r}
DT.filter <- subset(DT, subset=(Date >= "2007-02-01" & Date <= "2007-02-02"))
rm(DT)
```
## Converting dates
```{r}
datetime <- paste(as.Date(DT.filter$Date), DT.filter$Time)
DT.filter$Datetime <- as.POSIXct(datetime)
```
#plot the graph with legends
```{r}
par(mfrow=c(2,2), mar=c(4,4,2,1), oma=c(0,0,2,0))
with(DT.filter, {
  plot(Global_active_power~Datetime, type="l",
       ylab="Global Active Power", xlab="")
  plot(Voltage~Datetime, type="l",
       ylab="Voltage (volt)", xlab="datetime")
  plot(Sub_metering_1~Datetime, type="l",
       ylab="Energy sub metering", xlab="")
       lines(Sub_metering_2~Datetime,col='Red')
       lines(Sub_metering_3~Datetime,col='Blue')
       legend("topright", col=c("black", "red", "blue"), lty=1, lwd=2, bty="n", legend=c("Sub_metering_1", "Sub_metering_2", "Sub_metering_3"), cex = 0.75)
  plot(Global_reactive_power~Datetime, type="l",
       ylab="Global_Rective_Power",xlab="datetime")
})
```
## Saving to file
```{r}
dev.copy(png, file="plot4.png", height=480, width=480)
dev.off()
```
## Converting dates

```{r}
datetime <- paste(as.Date(DT.filter$Date), DT.filter$Time)
DT.filter$Datetime <- as.POSIXct(datetime)
```
#output histogram to PNG
```{r}
plot(DT.filter$Global_active_power~DT.filter$Datetime, type="l",
     ylab="Global Active Power (kilowatts)", xlab="")
dev.copy(png, file="plot2.png", height=480, width=480)

dev.off()
```
#plot the graph with legends
```{r}
with(DT.filter, {
  plot(Sub_metering_1~Datetime, type="l",
       ylab="Energy sub metering", xlab="")
  lines(Sub_metering_2~Datetime,col='Red')
  lines(Sub_metering_3~Datetime,col='Blue')
})
legend("topright", col=c("black", "red", "blue"), lty=1, lwd=2,
       legend=c("Sub_metering_1", "Sub_metering_2", "Sub_metering_3"), cex = 0.75)
```
## output histogram to PNG
```{r}
dev.copy(png, file="plot3.png", height=480, width=480)
dev.off()
```
#plot the graph with legends
```{r}
par(mfrow=c(2,2), mar=c(4,4,2,1), oma=c(0,0,2,0))
with(DT.filter, {
  plot(Global_active_power~Datetime, type="l",
       ylab="Global Active Power", xlab="")
  plot(Voltage~Datetime, type="l",
       ylab="Voltage (volt)", xlab="datetime")
  plot(Sub_metering_1~Datetime, type="l",
       ylab="Energy sub metering", xlab="")
       lines(Sub_metering_2~Datetime,col='Red')
       lines(Sub_metering_3~Datetime,col='Blue')
       legend("topright", col=c("black", "red", "blue"), lty=1, lwd=2, bty="n", legend=c("Sub_metering_1", "Sub_metering_2", "Sub_metering_3"), cex = 0.75)
  plot(Global_reactive_power~Datetime, type="l",
       ylab="Global_Rective_Power",xlab="datetime")
})
```
## Saving to file
```{r}
dev.copy(png, file="plot4.png", height=480, width=480)
dev.off()
```










